---
title: "informant R"
author: 'Leshu Zhou   Uni ID: 781066521 / lzho679'
date: "2024-05-02"
output: html_document
---
```{r}
library(dplyr)
```


```{r}
informant <- read.csv("simu_informant.csv")
informant <- informant %>%
  arrange(HOUSEID, PARTICID)
```


# MISS1
```{r}
informant <- informant %>%
  mutate(MISS1 = rowSums(select(., MENTAL, MEMORY, PUT, KEPT, FRDNAME, FAMNAME, CONVERS, 
                                WORDFIND, WORDWRG, PAST, LASTSEE, LASTDAY, ORIENT, 
                                LOSTOUT, LOSTIN, CHORES, HOBBY, MONEY, CHANGE, REASON) == 9, na.rm = TRUE),
         MISS3 = rowSums(select(., FEED, DRESS, TOILET) == 9, na.rm = T),
         MISSTOT = MISS3 * 3 + MISS1)

```




# RECODE  (1=0.5) (2=1)
```{r}
vars <- c("PUT", "KEPT", "FRDNAME", "FAMNAME", "CONVERS", 
          "WORDFIND", "WORDWRG", "PAST", "LASTSEE", "LASTDAY", "ORIENT", 
          "LOSTOUT", "LOSTIN", "CHORES", "CHANGE", "MONEY")

informant <- informant %>%
  mutate(across(all_of(vars), 
                ~ case_when(.x == 1 ~ 0.5, 
                            .x == 2 ~ 1, 
                            TRUE ~ .x)))
```


# do if   
```{r}
informant <- informant %>%
  mutate(DRESS = ifelse(DRESSDIS == 1, 0, DRESS),
         CHORES = ifelse(CHOREDIS == 1, 0, CHORES),
         FEED = ifelse(FEEDDIS == 1, 0, FEED),
         TOILET = ifelse(TOILDIS == 1, 0, TOILET))


```

# relscore
```{r}
informant <- informant %>%
  mutate(RELSOCRE = (30/(30 - MISSTOT)) * ((ACTIV + MENTAL + MEMORY + PUT + KEPT + FRDNAME + FAMNAME + 
                                              CONVERS + WORDFIND + WORDWRG + PAST + LASTSEE + LASTDAY + 
                                              ORIENT + LOSTOUT + LOSTIN + CHORES + HOBBY + MONEY + CHANGE + 
                                              REASON + FEED + DRESS + TOILET) - ((MISS1 + MISS3) * 9)))

```
# short version : RELSCORE= as.numeric(ACTIV)+ as.numeric(MENTAL)+ as.numeric(MEMORY)+ as.numeric(PUT)/2+ as.numeric(KEPT)/2+ as.numeric(FRDNAME)/2+ as.numeric(FAMNAME)/2+ as.numeric(CONVERS)/2+ as.numeric(WORDFIND)/2+ as.numeric(WORDWRG)/2+ as.numeric(PAST)/2+ as.numeric(LASTSEE)/2+ as.numeric(LASTDAY)/2+ as.numeric(ORIENT)/2+ as.numeric(LOSTOUT)/2+ as.numeric(LOSTIN)/2+ as.numeric(CHORESUM)+ as.numeric(HOBBY)+ as.numeric(MONEY)/2+ as.numeric(CHANGE)/2+ as.numeric(REASON)+ as.numeric(FEEDSUM)+ as.numeric(DRESSSUM)+ as.numeric(TOILETSUM)+ as.numeric(MISTAKE)+ as.numeric(DECIDE)+ as.numeric(MUDDLED))

# lr
```{r}
informant <- informant %>%
  mutate(LR = case_when(RELSOCRE <= 2.49 ~ 0.04,
                        RELSOCRE>= 2.5 & RELSOCRE <= 6.49 ~ 0.2,
                        RELSOCRE>= 6.5 & RELSOCRE <= 9.49 ~ 2.6,
                        RELSOCRE>= 9.5 & RELSOCRE <= 12.49 ~ 11.8,
                        RELSOCRE>= 12.5 & RELSOCRE <= 17.49 ~ 38.4,
                        RELSOCRE >= 17.5 ~ 113.7))

```

# recode same vars   (1=2)  (0.5=1)
```{r}
informant <- informant %>%
  mutate(across(all_of(vars), 
                ~ case_when(.x == 1 ~ 2, 
                            .x == 0.5 ~ 1, 
                            TRUE ~ .x)))


```

# SEQTOT & SRQCASE
```{r}
informant <- informant %>%
   mutate(SRQTOT = rowSums(select(., SRQ1, SRQ2, SRQ3, SRQ4, SRQ5, SRQ6, SRQ7, SRQ8, SRQ9, SRQ10,
                                  SRQ11, SRQ12, SRQ13, SRQ14, SRQ15, SRQ16, SRQ17, SRQ18, SRQ19, SRQ20) == 1, na.rm = TRUE))


attr(informant$SRQTOT, "label") <- "total srq score"

informant <- informant %>%
  mutate(SRQCASE = case_when(SRQTOT >= 0 & SRQTOT <= 7 ~ 0,
                             SRQTOT >= 8 ~ 1))
```


# zbmiss
```{r}
informant <- informant %>%
  mutate(ZBMISS = rowSums(select(., ZB1, ZB2, ZB3, ZB4, ZB5, ZB6, ZB7, ZB8, ZB9, ZB10,
                                  ZB11, ZB12, ZB13, ZB14, ZB15, ZB16, ZB17, ZB18, ZB19, ZB20,
                                  ZB21, ZB22) == 9, na.rm = TRUE),
         ZBTOT = (22 / (22 - ZBMISS)) * ((ZB1 + ZB2 + ZB3 + ZB4 + ZB5 + ZB6 + ZB7 + ZB8 + ZB9 + ZB10 + ZB11 + ZB12 + 
                                          ZB13 + ZB14 + ZB15 + ZB16 + ZB17 + ZB18 + ZB19 + ZB20 + ZB21 + ZB22) - (ZBMISS * 9)))



informant <- informant %>%
  mutate(across(c(ZB1, ZB2, ZB3, ZB4, ZB5, ZB6, ZB7, ZB8, ZB9, ZB10, ZB11, 
                  ZB12, ZB13, ZB14, ZB15, ZB16, ZB17, ZB18, ZB19, ZB20, ZB21, ZB22),
                ~ ifelse(.x == 9, NA, .x)))
```


# IF c_var
```{r}
informant <- informant %>%
  mutate(C_FAMILY = case_when(CBNTYPE1 == 4 ~ CBEN1,
                              CBNTYPE2 == 4 ~ CBEN2,
                              CBNTYPE3 == 4 ~ CBEN3,
                              CBNTYPE4 == 4 ~ CBEN4),
         C_GOV = case_when(CBNTYPE1 == 1 ~ CBEN1,
                           CBNTYPE2 == 1 ~ CBEN2,
                           CBNTYPE3 == 1 ~ CBEN3,
                           CBNTYPE4 == 1 ~ CBEN4),
         C_OCCUP = case_when(CBNTYPE1 == 2 ~ CBEN1,
                             CBNTYPE2 == 2 ~ CBEN2,
                             CBNTYPE3 == 2 ~ CBEN3,
                             CBNTYPE4 == 2 ~ CBEN4),
         C_DISAB = case_when(CBNTYPE1 == 3 ~ CBEN1,
                             CBNTYPE2 == 3 ~ CBEN2,
                             CBNTYPE3 == 3 ~ CBEN3,
                             CBNTYPE4 == 3 ~ CBEN4),
         C_RENT = case_when(CBNTYPE1 == 5 ~ CBEN1,
                            CBNTYPE2 == 5 ~ CBEN2,
                            CBNTYPE3 == 5 ~ CBEN3,
                            CBNTYPE4 == 5 ~ CBEN4),
         C_WORK = case_when(CBNTYPE1 == 6 ~ CBEN1,
                            CBNTYPE2 == 6 ~ CBEN2,
                            CBNTYPE3 == 6 ~ CBEN3,
                            CBNTYPE4 == 6 ~ CBEN4),
         C_CARE = case_when(CBNTYPE1 == 7 ~ CBEN1,
                            CBNTYPE2 == 7 ~ CBEN2,
                            CBNTYPE3 == 7 ~ CBEN3,
                            CBNTYPE4 == 7 ~ CBEN4),
         C_OTH = case_when(CBNTYPE1 == 8 ~ CBEN1,
                           CBNTYPE2 == 8 ~ CBEN2,
                           CBNTYPE3 == 8 ~ CBEN3,
                           CBNTYPE4 == 8 ~ CBEN4))


informant <- informant %>%
  mutate(across(c(C_FAMILY, C_GOV, C_OCCUP, C_DISAB, C_RENT, C_WORK, C_CARE, C_OTH),
                ~ ifelse(is.na(.x), 0, .x)))
```



# compute
```{r}
informant <- informant %>%
  mutate(CNOF_TOT = C_GOV + C_OCCUP + C_DISAB + C_RENT + C_WORK + C_CARE + C_OTH,
         C_TOT = CNOF_TOT + C_FAMILY,
         TW_DEP = 1.5 * (AM1 + PM1 + EVE1 + NITE1 + AM2 + PM2 + EVE2 + NITE2))

```


# recode
```{r}
informant <- informant %>%
  mutate(across(c(CASHRS2, CASHRS3, CASHRS4, CASHRS5, CASHRS7, CASHRS8),
                ~ ifelse(is.na(.x) | .x == 9, 0, .x)))

informant <- informant %>%
  mutate(across(c(CASHRS1, CASHRS6),
                ~ ifelse(is.na(.x) | .x == 99, 0, .x)),
         TADL = CASHRS2 + CASHRS3 + CASHRS4 + CASHRS5 + CASHRS7 + CASHRS8)

```




# do if
```{r}
informant <- informant %>%
  mutate(NPI1SEV = ifelse(NPI1 == 0 & is.na(NPI1SEV), 0, NPI1SEV),
         NPI1D = ifelse(NPI1 == 0 & is.na(NPI1D), 0, NPI1D),
         
         NPI2SEV = ifelse(NPI2 == 0 & is.na(NPI2SEV), 0, NPI2SEV),
         NPI2DIS = ifelse(NPI2 == 0 & is.na(NPI2DIS), 0, NPI2DIS),
         
         NPI3SEV = ifelse(NPI3 == 0 & is.na(NPI3SEV), 0, NPI3SEV),
         NPI3DIS = ifelse(NPI3 == 0 & is.na(NPI3DIS), 0, NPI3DIS),
         
         NPI4SEV = ifelse(NPI4 == 0 & is.na(NPI4SEV), 0, NPI4SEV),
         NPI4DIS = ifelse(NPI4 == 0 & is.na(NPI4DIS), 0, NPI4DIS),
         
         NPI5SEV = ifelse(NPI5 == 0 & is.na(NPI5SEV), 0, NPI5SEV),
         NPI5DIS = ifelse(NPI5 == 0 & is.na(NPI5DIS), 0, NPI5DIS),
         
         NPI6SEV = ifelse(NPI6 == 0 & is.na(NPI6SEV), 0, NPI6SEV),
         NPI6DIS = ifelse(NPI6 == 0 & is.na(NPI6DIS), 0, NPI6DIS),
         
         NPI7SEV = ifelse(NPI7 == 0 & is.na(NPI7SEV), 0, NPI7SEV),
         NPI7DIS = ifelse(NPI7 == 0 & is.na(NPI7DIS), 0, NPI7DIS),
         
         NPI8SEV = ifelse(NPI8 == 0 & is.na(NPI8SEV), 0, NPI8SEV),
         NPI8DIS = ifelse(NPI8 == 0 & is.na(NPI8DIS), 0, NPI8DIS),
         
         NPI9SEV = ifelse(NPI9 == 0 & is.na(NPI9SEV), 0, NPI9SEV),
         NPI9DIS = ifelse(NPI9 == 0 & is.na(NPI9DIS), 0, NPI9DIS),
         
         NPI10SEV = ifelse(NPI10 == 0 & is.na(NPI10SEV), 0, NPI10SEV),
         NPI10DIS = ifelse(NPI10 == 0 & is.na(NPI10DIS), 0, NPI10DIS),
         
         NPI11SEV = ifelse(NPI11 == 0 & is.na(NPI11SEV), 0, NPI11SEV),
         NPI11DIS = ifelse(NPI11 == 0 & is.na(NPI11DIS), 0, NPI11DIS),
         
         NPI12SEV = ifelse(NPI12 == 0 & is.na(NPI12SEV), 0, NPI12SEV),
         NPI12DIS = ifelse(NPI12 == 0 & is.na(NPI12DIS), 0, NPI12DIS))


```





```{r}
vars2 <- c("NPI1", "NPI1SEV", "NPI1D", 
           "NPI2", "NPI2SEV", "NPI2DIS",
           "NPI3", "NPI3SEV", "NPI3DIS",
           "NPI4", "NPI4SEV", "NPI4DIS",
           "NPI5", "NPI5SEV", "NPI5DIS",
           "NPI6", "NPI6SEV", "NPI6DIS",
           "NPI7", "NPI7SEV", "NPI7DIS",
           "NPI8", "NPI8SEV", "NPI8DIS",
           "NPI9", "NPI9SEV", "NPI9DIS",
           "NPI10", "NPI10SEV", "NPI10DIS",
           "NPI11", "NPI11SEV", "NPI11DIS",
           "NPI12", "NPI12SEV", "NPI12DIS")

informant <- informant %>%
  mutate(across(all_of(vars2), 
                ~ case_when(.x == 9 ~ NA, 
                            TRUE ~ .x)),
         NPISEV = NPI1SEV + NPI2SEV + NPI3SEV + NPI4SEV + NPI5SEV + NPI6SEV + 
                  NPI7SEV + NPI8SEV + NPI9SEV + NPI10SEV + NPI11SEV + NPI12SEV,
         NPIDIS = NPI1D + NPI2DIS + NPI3DIS + NPI4DIS + NPI5DIS + NPI6DIS + 
                  NPI7DIS + NPI8DIS + NPI9DIS + NPI10DIS + NPI11DIS + NPI12DIS)

```


```{r}
write.table(informant, file = "simu_informantR.csv", sep = ",", row.names = F)


```

















